---
title: "Untitled"
output: github_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Link to githup repository  

## Required Packages  

```{r setup packages results='hide'}
library(tidyverse)
library(httr)
library(jsonlite)
```

## Write functions to contact the NHL Records API  
```{r Parsed Franchise}
#function returns id, first seasonid, and last seasonid and name of every team in the history of the NHL
#https://records.nhl.com/site/api/franchise/ 
#Filter by common name
#https://records.nhl.com/site/api/franchise?cayenneExp=teamCommonName=%22Wanderers%22
#Filter by franchise ID


fBase<- "https://records.nhl.com/site/api/"
fEndpoint<- "franchise"
fCallURL<- paste(fBase,fEndpoint, sep="")
fRawJSON<- GET(fCallURL)
fJSON_text<- content(fRawJSON, "text")
fParsedText <- fromJSON(fJSON_text, flatten = TRUE)
fDF <- as.data.frame(fParsedText)

```

```{r Parsed team totals}
#function Returns total stats for every franchise (ex roadTies, roadWins, etc)
#/franchise-team-totals Total stats for every franchise (ex roadTies, roadWins, etc)
#https://records.nhl.com/site/api/franchise-team-totals

```

```{r Parsed Franchise Season Records}
#season records for a specific franchise
#https://records.nhl.com/site/api/franchise-season-records?cayenneExp=franchiseId=ID

#example query
#/franchise-season-results?cayenneExp=franchiseId=24&sort=seasonId&dir=DESC Returns every season result for a specified team, sorted by seasonId in descending order

```

```{r Parsed Goalie Records}
#Goalie records for the specified franchise 

#/franchise-goalie-records?cayenneExp=franchiseId=ID
```


```{r Parsed Skater Records}
#/franchise-skater-records?cayenneExp=franchiseId=ID Skater records, same interaction as goalie endpoint

```

```{r Stats API All}
#You should have a function to return parsed data for the following endpoint from the stats API(the user should be able to specify values for any of the eight modifiers listed):∗https://statsapi.web.nhl.com/api/v1/teams
```

```{r One-Stop-Wrapper Function}
```

##Example Analysis


## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
