---
title: "NHL API Interface"
output: 
  github_document:
    toc: TRUE
    toc_depth: 3
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Link to github repository  

## Required Packages  

```{r setup packages, results="hide", message = FALSE}
library(tidyverse)
library(httr)
library(jsonlite)
library(knitr)
```

# Functions to contact the NHL Records API  
Note -- to help with ease of tracking variable scope -- function arguments have the letter 'a' for a prefix, variables local to the function have an 'f' for a prefix.  Global variables have a 'g' prefix.
```{r Filter Functions}

#Returns first partial matching entry, unsorted, from input conditions
pullIDDecoder<- function(aName = "", aTeamID= "", aFranchiseID = "") 
{
  #Run a pull against the franchise table to get the full decoding
  fBase<- "https://records.nhl.com/site/api/"
  fEndpoint<- "franchise"
  fCallURL<- paste0(fBase,fEndpoint)
  

  fRawJSON<- GET(fCallURL)
  fJSON_text<- content(fRawJSON, "text")
  fParsedText <- fromJSON(fJSON_text, flatten = TRUE)
  fDF <- as.data.frame(fParsedText)
  
  fTeamList<- as_tibble(fDF)%>%
    filter(toupper(data.teamCommonName) == toupper(aName) | data.id == aFranchiseID | data.mostRecentTeamId == aTeamID)
  
  fDecoder <- list("TeamID" = toString(fTeamList$data.mostRecentTeamId[1]), "FranchiseID" = toString(fTeamList$data.id[1]))
  fDecoder <- lapply(fDecoder, FUN=sub, pattern = "NA", replacement = "")
  
  return(fDecoder)
}

```

```{r Parsed Franchise, warning=FALSE}
#input options for franchise common name, franchise id number, and teamid 
#function returns id, first seasonid, and last seasonid and name of every team in the history of the NHL
getFranchiseInfo<- function(aName = "", aTeamID= "", aFranchiseID = ""){
#Define API url and pull results
fBase<- "https://records.nhl.com/site/api/"
fEndpoint<- "franchise"

#Process our inputs.  If any is non-empty, we need to add a query modifier.
#Choosing to query for FranchiseID, but could easily pull on mostRecentTeamID
fCayenneExp = ""
if(aName!="" | aTeamID != "" | aFranchiseID !="") fCayenneExp <- pullIDDecoder(aName, aTeamID, aFranchiseID)$FranchiseID
#Append the appropriate prefix for this base & endpoint
if(fCayenneExp != "") fCayenneExp <-paste0("?cayenneExp=id=",fCayenneExp)

#Pull API Data
fCallURL<- paste0(fBase,fEndpoint,fCayenneExp)

#Process results into a dataframe and return
fRawJSON<- GET(fCallURL)
fJSON_text<- content(fRawJSON, "text")
fParsedText <- fromJSON(fJSON_text, flatten = TRUE)
fDF <- as.data.frame(fParsedText)

return(fDF)
}
```

```{r Parsed team totals}
#input options for franchise common name and franchise team id number, number runs slightly faster
#function Returns total stats for every franchise (ex roadTies, roadWins, etc)
getFranchiseTotals<- function(aName = "", aTeamID= "", aFranchiseID = ""){
#Define API url and pull results
fBase<- "https://records.nhl.com/site/api/"
fEndpoint<- "franchise-team-totals"

#Process our inputs.  If any is non-empty, we need to add a query modifier.
#Need to pull for FranchiseID
fCayenneExp = ""
if(aName!="" | aTeamID != "" | aFranchiseID !="") fCayenneExp <- pullIDDecoder(aName, aTeamID, aFranchiseID)$FranchiseID
#Append the appropriate prefix for this base & endpoint
if(fCayenneExp != "") fCayenneExp <-paste0("?cayenneExp=franchiseId=",fCayenneExp)

fCallURL<- paste0(fBase,fEndpoint,fCayenneExp)

#Process results into a dataframe and return
fRawJSON<- GET(fCallURL)
fJSON_text<- content(fRawJSON, "text")
fParsedText <- fromJSON(fJSON_text, flatten = TRUE)
fDF <- as.data.frame(fParsedText)

return(fDF)
}
```

```{r Parsed Franchise Season Records}
getFranchiseSeasonRecords<- function(aName = "", aTeamID= "", aFranchiseID = ""){
#Define API url and pull results
fBase<- "https://records.nhl.com/site/api/"
fEndpoint<- "franchise-season-records"

#Process our inputs.  If any is non-empty, we need to add a query modifier.
#Need to pull for FranchiseID
fCayenneExp = ""
if(aName!="" | aTeamID != "" | aFranchiseID !="") fCayenneExp <- pullIDDecoder(aName, aTeamID, aFranchiseID)$FranchiseID
#Append the appropriate prefix for this base & endpoint
if(fCayenneExp != "") fCayenneExp <-paste0("?cayenneExp=franchiseId=",fCayenneExp)

fCallURL<- paste0(fBase,fEndpoint,fCayenneExp)

#Process results into a dataframe and return
fRawJSON<- GET(fCallURL)
fJSON_text<- content(fRawJSON, "text")
fParsedText <- fromJSON(fJSON_text, flatten = TRUE)
fDF <- as.data.frame(fParsedText)

return(fDF)
}
```

```{r Parsed Goalie Records}
#Goalie records for the specified franchise 
#/franchise-goalie-records?cayenneExp=franchiseId=ID
getFranchiseGoalieRecords<- function(aName = "", aTeamID= "", aFranchiseID = ""){
#Define API url and pull results
fBase<- "https://records.nhl.com/site/api/"
fEndpoint<- "franchise-goalie-records"

#Process our inputs.  If any is non-empty, we need to add a query modifier.
#Need to pull for FranchiseID
fCayenneExp = ""
if(aName!="" | aTeamID != "" | aFranchiseID !="") fCayenneExp <- pullIDDecoder(aName, aTeamID, aFranchiseID)$FranchiseID
#Append the appropriate prefix for this base & endpoint
if(fCayenneExp != "") fCayenneExp <-paste0("?cayenneExp=franchiseId=",fCayenneExp)

fCallURL<- paste0(fBase,fEndpoint,fCayenneExp)

#Process results into a dataframe and return
fRawJSON<- GET(fCallURL)
fJSON_text<- content(fRawJSON, "text")
fParsedText <- fromJSON(fJSON_text, flatten = TRUE)
fDF <- as.data.frame(fParsedText)

return(fDF)
}
```


```{r Parsed Skater Records}
#/franchise-skater-records?cayenneExp=franchiseId=ID Skater records, same interaction as goalie endpoint
getFranchiseSkaterRecords<- function(aName = "", aTeamID= "", aFranchiseID = ""){
#Define API url and pull results
fBase<- "https://records.nhl.com/site/api/"
fEndpoint<- "franchise-skater-records"

#Process our inputs.  If any is non-empty, we need to add a query modifier.
#Need to pull for FranchiseID
fCayenneExp = ""
if(aName!="" | aTeamID != "" | aFranchiseID !="") fCayenneExp <- pullIDDecoder(aName, aTeamID, aFranchiseID)$FranchiseID
#Append the appropriate prefix for this base & endpoint
if(fCayenneExp != "") fCayenneExp <-paste0("?cayenneExp=franchiseId=",fCayenneExp)

fCallURL<- paste0(fBase,fEndpoint,fCayenneExp)

#Process results into a dataframe and return
fRawJSON<- GET(fCallURL)
fJSON_text<- content(fRawJSON, "text")
fParsedText <- fromJSON(fJSON_text, flatten = TRUE)
fDF <- as.data.frame(fParsedText)

return(fDF)
}
```

```{r TestRecordsAPI}
#Available for validation
#gdfFranchiseAll<-getFranchiseInfo()
#gdfFranchiseName<-getFranchiseInfo(aName="Devils")
#gdfFranchiseNumber<-getFranchiseInfo(aFranchiseID = 2)
#gdfFranchiseTeam<-getFranchiseInfo(aTeamID = 2)

#gdfFranTotal<-getFranchiseTotals()
#gdfFranTotalName<-getFranchiseTotals(aName="Devils")
#gdfFranTotalNumber<-getFranchiseTotals(aFranchiseID = 2)
#gdfFranTotalTeam<-getFranchiseTotals(aTeamID = 2)

#gdfFranSeas<-getFranchiseSeasonRecords()
#gdfFranSeasName<-getFranchiseSeasonRecords(aName="Devils")
#gdfFranSeasNumber<-getFranchiseSeasonRecords(aFranchiseID = 2)
#gdfFranSeasTeam<-getFranchiseSeasonRecords(aTeamID = 2)

#gdfFranGoal<-getFranchiseGoalieRecords()
#gdfFranGoalName<-getFranchiseGoalieRecords(aName="Devils")
#gdfFranGoalNumber<-getFranchiseGoalieRecords(aFranchiseID = 2)
#gdfFranGoalTeam<-getFranchiseGoalieRecords(aTeamID = 2)

#gdfFranSkat<-getFranchiseSkaterRecords()
#gdfFranSkatName<-getFranchiseSkaterRecords(aName="Devils")
#gdfFranSkatNumber<-getFranchiseSkaterRecords(aFranchiseID = 2)
#gdfFranSkatTeam<-getFranchiseSkaterRecords(aTeamID = 2)

```
```{r Stats Filter}
#Need a different filter function for the different API set.
#This version needs to resolve 
```
```{r Stats API All}
ProcessExpandArgs<- function(aExpand, aTeams)
{
  fExpand<- toupper(aExpand)
  if(fExpand == "") return("")
  if(fExpand == "ROSTER") return("?expand=team.roster")
  if(fExpand == "EZROSTER") return("?expand=person.names")
  if(fExpand == "NEXTSCHED") return("?expand=team.schedule.next")
  if(fExpand == "PREVSCHED") return("?expand=team.schedule.previous")
  if(fExpand == "STATS") return("?expand=team.stats")
  if(fExpand == "TEAMLIST") return(paste0("?teamId=", aTeams))
}


#You should have a function to return parsed data for the following endpoint from the stats API(the user should be able to specify values for any of the eight modifiers listed):∗https://statsapi.web.nhl.com/api/v1/teams

#aExpand can take the following values, pulling different summary expansions:
  #"Roster", "EZRoster", "NextSched","PrevSched","Stats", "TeamList",  ""
  #Note that the TeamList value needs valid teamIDs, and that the common inputs of aName and aNumber supersede this command

#aSeason is a string formatted Y111Y222 restricting the pull to the season of interest.
#By default, an empty string will pull the current season where applicable
#Example:  20142015 to refer to the 2014-2015 hockey season.

#aTeams is a comma separated string of teamIDs and requires the 'TeamList' expansion instruction 
#Example: "4,5,29"
#Note that the common inputs of aName, aTeamID, and aFranchiseID supersede this field
getTeamStats<- function(aExpand="", aSeason = "", aTeams = "", 
                        aName = "", aTeamID= "", aFranchiseID = "")
{
  #Process our inputs.  If any is non-empty, we need to add a query modifier.
  #Check for a common input
  fTeamStr = ""
  if(aName!="" | aTeamID != "" | aFranchiseID !="")
    {fTeamStr <- pullIDDecoder(aName, aTeamID, aFranchiseID)$TeamID}
  #Append the appropriate prefix for this base & endpoint
  if(fTeamStr != "") fTeamStr <-paste0("/",fTeamStr)
  
    #Process aExpand and aTeams where relevant
    fExpand<- ProcessExpandArgs(aExpand, aTeams)
      
    #process aSeason
    fSeason=if(aSeason != ""){
      #If we already have a modifier, we need to tack this on with an &
      if(fExpand!="") paste0("&season=", aSeason)
      #else we need to use this as a direct modifier
      else paste0("?season=", aSeason)
    }

  #Define API url and pull results
  fBase<- "https://statsapi.web.nhl.com/api/v1/"
  fEndpoint<- "teams"

  fCallURL<- paste0(fBase,fEndpoint,fTeamStr,fExpand,fSeason)
  print(fCallURL)

  #Process results into a dataframe and return
  fRawJSON<- GET(fCallURL)
  fJSON_text<- content(fRawJSON, "text")
  fParsedText <- fromJSON(fJSON_text, flatten = TRUE)
  fDF <- as.data.frame(fParsedText)

  return(fDF)
}

#Available for validation
#gdfTeamStatsa<- getTeamStats(aExpand = "Roster")
#gdfTeamStatsb<- getTeamStats(aExpand = "EZRoster")
#gdfTeamStatsc<- getTeamStats(aExpand = "NextSched")
#gdfTeamStatsd<- getTeamStats(aExpand = "PrevSChed")
#gdfTeamStatse<- getTeamStats(aExpand = "Stats")
#gdfTeamStatsf<- getTeamStats(aExpand = "Teamlist", aTeams = "4,5,7")
#gdfTeamStatsg<- getTeamStats(aSeason = "20142015")
#gdfTeamStatsh<- getTeamStats(aExpand = "Stats", aSeason = "20142015")
#gdfTeamStatsi<- getTeamStats(aName = "Devils")
#gdfTeamStatsj<- getTeamStats(aFranchiseID = 2)
#gdfTeamStatsk<- getTeamStats(aTeamID = 2)
#gdfTeamStatsl<- getTeamStats(aTeamID = "2", aTeams = "4,5,7")

#gdfTeamStatsm<-getTeamStats(aName="Devils")
#gdfTeamStatsn<-getTeamStats(aFranchiseID = 2)
#gdfTeamStatso<-getTeamStats(aTeamID = 2)
#gdfTeamStatsp<-getTeamStats()


```

```{r One-Stop-Wrapper Function}
pullNHLAPI<- function(aEndpoint = "", ...){
  #If we don't have any inputs, print out instructions
  #Also pull the default franchise decoder
  if(aEndpoint == ""){
    print("Please rerun with a specific endpoint chosen. Options are: ")
    print("FranchiseInfo")
    print("FranchiseTotals")
    print("FranchiseSeasonRecords")
    print("FranchiseGoalieRecords")
    print("FranchiseSkaterRecords")
    print("Team")
    print("")
    print("Common arguments to the queries are:")
    print("aName - common name of the team from FranchiseInfo pull")
    print("aTeamID - MostRecentTeamID from the FranchiseInfo pull")
    print("aFranchiseID - id field from the FranchiseInfo pull.")
    print("Note 1- aFranchiseID is constant for franchises relocating or changing names")
    print("Note 2- The \"Team\" Query has additional potential modifiers, please see vignette for more details")
    print("Vignette URL")
    return(getFranchiseInfo(...))}
  
    if(aEndpoint == "FranchiseInfo"){return(getFranchiseInfo(...))}
    if(aEndpoint == "FranchiseTotals"){return(getFranchiseTotals(...))}
    if(aEndpoint == "FranchiseSeasonRecords"){return(getFranchiseSeasonRecords(...))}
    if(aEndpoint == "FranchiseGoalieRecords"){return(getFranchiseGoalieRecords(...))}
    if(aEndpoint == "FranchiseSkaterRecords"){return(getFranchiseSkaterRecords(...))}
    if(aEndpoint == "Team"){return(getTeamStats(...))}
}

#Available for validation
#gdfWrap<- pullNHLAPI()
#gdfWrapa<- pullNHLAPI("FranchiseInfo")
#gdfWrapb<- pullNHLAPI("FranchiseTotals")
#gdfWrapc<- pullNHLAPI("FranchiseSeasonRecords")
#gdfWrapd<- pullNHLAPI("FranchiseGoalieRecords")
#gdfWrape<- pullNHLAPI("FranchiseSkaterRecords")
#gdfWrapf<- pullNHLAPI("Team",aName = "Devils")
#gdfWrapg<- pullNHLAPI("Team",aTeamID = 2)
#gdfWraph<- pullNHLAPI("Team",aFranchiseID = "2")
#gdfWrapi<- pullNHLAPI("Team")
#gdfWrapf<- pullNHLAPI("Team")
```

##Example Analysis  
Haven't followed Hockey too much.  From what I understand, it's mostly about scoring goals and checking people just hard enough that they don't put you in the penalty box.  Wayne Gretzky was a household name growing up.  Let's do some exploration for context about how good of a player he was.  

Data is available in the FranchiseSkaterRecords endpoint:  

```{r Analysis_1}
#Pull Data from API
gTibGretz<- as_tibble(pullNHLAPI("FranchiseSkaterRecords"))

#Flag the records that are associated with Wayne Gretzky
gTibGretz <- gTibGretz  %>% mutate(Gretzky = ifelse(data.lastName=="Gretzky" & data.firstName == "Wayne",
         "Wayne Gretzky", "Rest of League"))
```

First things first, there are probably a lot of alternates, rookies, and other folks that didn't get a lot of time on the ice in this pull. Let's take a look at the distribution of games played per season and filter them out.

```{r Low Playtime}
gTibGretz<- gTibGretz %>% mutate (GamesPerSeason = data.gamesPlayed / data.seasons)
g <- ggplot(data = gTibGretz, mapping = aes(x = GamesPerSeason))
g+ geom_histogram(binwidth = 1)+ggtitle("Games Per Season for Player Franchise Records")

#It's a fairly uniform density, but it looks like a second mode starts around 30 games.
#Let's filter out entries with <30 games/ season
gTibGretz <- gTibGretz %>% filter(GamesPerSeason >= 30)
```  

Ok, now let's figure out how scoring goals correlates to penalty time.  
```{r Penalty vs Scoring}
#Scatterplot to evaluate bivariate relationship
g<- ggplot(data = gTibGretz, mapping = aes (x= data.mostPenaltyMinutesOneSeason, y = data.mostGoalsOneSeason))
g+geom_point(mapping = (aes(colour = data.positionCode, shape = Gretzky, size = Gretzky))) + 
  ggtitle("Personal Bests at a Franchise, Goals vs Penalty Time by Player, All Time")
```
We see that Wayne had a clearly phenomenal tenure at one of his franchises, apparently still being the all time scoring leader for goals in a regular season by a significant margin across all franchises.  He was also apparently very good at not getting caught checking people, as his maximum penalty time at that franchise was less than any other center who scored more than 63 goals in one season.  

It also looks like there are four different clusters of exceptional players.  We have the Gretzky Group, who are  covert and high-scoring. These players score over 63 times in a season and have stayed under 100 minutes of penalties in a season. We also have the stadium fillers, this group is aggressive but score goals in the process.  They hang out in the penalty box 200-300 minutes in a season while scoring more than 38 goals in their best seasons.  Franchise owners probably love them, coaches probably hate them.  Second to last we have the defense and left wingers.  These guys just like hitting people and presumably remember to clear the puck from time to time.  Finally, we have some guy who managed to rack up 6 hours of penalty time in a single season -- one whole hour more than any other player has ever been tolerated by their coach.  Dave Schultz, from -- you guessed it -- Philadelphia.  

Here's the top 6 players for penalty times in a season:

```{r Max Penalty}
#Players with the most penalty minutes in a single season.
kable(head(gTibGretz%>% select(data.firstName, data.lastName, data.franchiseName, data.mostPenaltyMinutesOneSeason,            data.mostPenaltyMinutesSeasonIds)%>% arrange(desc((data.mostPenaltyMinutesOneSeason)))))
```
Alright, back to Wayne Gretzky.  We just saw that he was a center. How many skaters from different positions are we comparing against? We wouldn't want to compare that position against a defenseman for scoring. Let's generate average penalty time per game and and average goals per game to see how the different positions compare.

```{r Numerical Summaries}
#Mutate in Avg Penalty Time and Avg Goals per Game at a franchise
gTibGretz <-gTibGretz %>% mutate( penaltyMinPerGame = data.penaltyMinutes / data.gamesPlayed,
                                   goalsPerGame = data.goals/data.gamesPlayed)

gTibPositionSummary<- gTibGretz %>% group_by(data.positionCode, Gretzky) %>% 
  summarise(nPlayerFranchiseObs = n(), avgGoalsPerGame=mean(goalsPerGame),
            stdDevGoals = sd(goalsPerGame), avgPenaltyBoxPerGame = mean(penaltyMinPerGame),
            stdDevPenaltyBoxPerGame = sd(penaltyMinPerGame))

#Barchart vs Position
g<- ggplot(data = gTibPositionSummary, mapping= aes(x = data.positionCode,
                                        y = nPlayerFranchiseObs, fill = data.positionCode))
g + geom_bar( stat = 'identity' ) + ggtitle('Count of players vs position') +
  ylab('Number of Players This Position') + xlab('Position')

#Performance Summary for each position
kable(gTibPositionSummary, digits = 3)
```
From that quick summary, we see that Centers, Left Wingers, and Right Wingers are all roughly consistent for number of points scored.  Defensemen understandably score far less.  Just from the numerical summary, we do see that Gretzky averages 3 standard deviations over the league average for a center, quite impressive.  The distribution of penaltybox times is far noisier with a coefficient of variance close to 1.  Gretzky is ~36% below average compared to the other Centers.

Let's continue to look at where Gretzky falls relative to other offensive players.

```{r boxplots}
#Trim the defensive players from the set
gTibGretz <- gTibGretz %>% filter(data.positionCode%in% c('C', 'R', 'L'))

#Setup common variables for plotting
g<- ggplot(data = gTibGretz, mapping = aes(x = Gretzky, color = Gretzky))

#Individual Box Plots for several metrics
g + geom_boxplot(mapping = aes(y = goalsPerGame)) + ggtitle('Goals per Game') +
  geom_jitter(mapping = aes(y = goalsPerGame) )

g + geom_boxplot(mapping = aes(y = data.mostGoalsOneGame)) + ggtitle('Most Goals One Game') + 
  ylab('Goals in a Single Game') + geom_jitter(mapping = aes(y = data.mostGoalsOneGame))

g + geom_boxplot(mapping = aes(y = data.mostAssistsOneGame)) + ggtitle('Most Assists One Game') + 
  ylab('Assists in a Single Game') + geom_jitter(mapping = aes(y =data.mostAssistsOneGame))

g + geom_boxplot(mapping = aes(y = data.mostPointsOneGame)) + 
  ggtitle('Most Points One Game (Goals + Assists)') + ylab('Points in a Single Game') +
  geom_jitter(mapping = aes(y = data.mostPointsOneGame))

g + geom_boxplot(mapping = aes(y = penaltyMinPerGame)) + ggtitle('Average Penalty Time per Game (minutes)') + 
  ylab('Penalty Time per Game') + geom_jitter(mapping = aes(y = penaltyMinPerGame))

```
Clearly an exemplary player with numbers that are matched by few across his tenures at several franchises.  Let's see how his franchises performed

```{r Analysis_2}
#Figure out which teams Gretzky Played on, and filter data table down to those franchises
gTibGretzFranchList<- gTibGretz %>% group_by(Gretzky, data.franchiseId, data.franchiseName) %>%
  summarise(offensiveSkaterCount = n(), player.gamesPlayed = max(data.gamesPlayed))

#Print the teams
kable(gTibGretzFranchList%>%select(-offensiveSkaterCount)%>%filter(Gretzky =="Wayne Gretzky"))

#Join our Gretzky decoder to the franchise totals
gTibGretzkyFranch<-gTibGretzFranchList%>%
  inner_join(pullNHLAPI("FranchiseSeasonRecords"), by = "data.franchiseId")

gTibFranchSumm <- gTibGretzkyFranch %>% group_by(Gretzky) %>%
  summarise(franchiseCount = n(), averageMostGoals = mean(data.mostGoals), 
            stdDevMostGoals = sd(data.mostGoals), averageMostWins = mean(data.mostWins),
            stdDevMostWins = sd(data.mostWins), averagePenaltyTime = mean(data.mostPenaltyMinutes),
            stdDevPenaltyTime = sd(data.mostPenaltyMinutes))

kable(gTibFranchSumm, digits = 1)

g<- ggplot(data = gTibGretzkyFranch, mapping = aes(x=Gretzky))

g+geom_boxplot(mapping = aes(y = data.mostGoals)) + ggtitle("Most Franchise Goals in a Season -- All Time") + 
  geom_jitter(mapping =aes(y=data.mostGoals)) 

g+geom_boxplot(mapping = aes(y = data.mostWins)) + ggtitle("Most Franchise Wins in a Season -- All Time") + 
  geom_jitter(mapping =aes(y=data.mostWins)) + ylab('Most Wins')


```
These plots are a stretch, since we're not actually limited to the seasons where Gretzky was and was not playing for these franchises -- we're looking at all time records.  Still, I'd bet an all-time leading scorer was on the roster for at least of those franchise goal records.  For wins in a season, it looks like Gretzky's best team is in the top 7 while the others are more typical.

For one last look at his influence, let's see how many skaters were named Wayne in the 2000s.

```{r Named Wayne}
#Pull a fresh, untrimmed set of skater data.  
gTibWayne<- as_tibble(pullNHLAPI("FranchiseSkaterRecords"))
#Add two factor columns for name and rough date ~20 years after Gretzky joined the Oilers
gTibWayne<- gTibWayne %>%  mutate(NamedWayne = ifelse(data.firstName == 'Wayne',"Wayne", "Not Wayne"), 
         After2000 = ifelse(as.numeric(substr(data.mostPointsSeasonIds,1,4)) > 2000, 
                            "Later than 2000", "Before 2000"))

table(gTibWayne$NamedWayne, gTibWayne$After2000)
```
Well, it looks like the name Wayne has not shot up in popularity in the years since Gretzky became famous.  I guess that just makes Gretzky that much more unique.
