---
title: "NHL API Interface"
output: 
  github_document:
    toc: TRUE
    toc_depth: 3
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Overview  
  This vignette implements several functions to access the NHL API using R, and rounds through an example analysis of Wayne Gretzky's franchise stats.  This is a limited implementation of the API, and far more data is available for future development and analysis.  

  Note when viewing this code-- to help with ease of tracking variable scope -- function arguments have the letter 'a' for a prefix, variables local to the function have an 'f' for a prefix.  Global variables have a 'g' prefix.  

# Repository and Blog  
[Repository](https://github.com/fd54386/NHL-API-Interface)  
[Blogpost](https://fd54386.github.io/)

# Required Packages  
  To run this code, you will need to install the tidyverse, httr, jsonlite, and knitr packages 
```{r setup packages, results="hide", message = FALSE}
library(tidyverse)
library(httr)
library(jsonlite)
library(knitr)
```
# Project Functions  

### Helper Function  
  This function would be private if this were a class.  It's used to tie the common arguments of `aName`, `aTeamId`, and `aFranchiseId` together. 

```{r Filter Functions}
#Returns first partial matching entry, unsorted, from input conditions
pullIDDecoder<- function(aName = "", aTeamId= "", aFranchiseId = "") 
{
  #Run a pull against the franchise table to get the full decoding
  fBase<- "https://records.nhl.com/site/api/"
  fEndpoint<- "franchise"
  fCallURL<- paste0(fBase,fEndpoint)
  
  #Parse results to dataframe
  fRawJSON<- GET(fCallURL)
  fJSON_text<- content(fRawJSON, "text")
  fParsedText <- fromJSON(fJSON_text, flatten = TRUE)
  fDF <- as.data.frame(fParsedText)
  
  #Filter for the called arguments
  fTeamList<- as_tibble(fDF)%>%
    filter(toupper(data.teamCommonName) == toupper(aName) | data.id == aFranchiseId |
             data.mostRecentTeamId == aTeamId)
  
  #If we didn't get any rows returned from that filter (ie -- no arguments specified)
  #Trim the NA values
  fDecoder <- list("TeamID" = toString(fTeamList$data.mostRecentTeamId[1]), "FranchiseID" = 
                     toString(fTeamList$data.id[1]))
  fDecoder <- lapply(fDecoder, FUN=sub, pattern = "NA", replacement = "")
  #Return the team and franchise Ids, need both for different endpoints
  return(fDecoder)
}
```

## Functions to contact the NHL Records API  
  We have written 6 functions to contact the NHL API.  There is also a wrapper function to help access all of the endpoints from a single function if you don't like autocomplete.  

  There are 3 common arguments to all of these functions.  `aName` refers to the team common name, found in the records Franchise endpoint. `aFranchiseId` and `aTeamId` are different keys for teams. `aFranchiseId` will be constant across name changes and city relocations while `aTeamId` changes for each.  All have comparable runtime, and will filter for only 1 result.  

### Franchise Info  
  This is the default call of the wrapper function.  It's a convenient decoder for common name, franchiseID (first ID column) and TeamID (data.mostRecentTeamID)

```{r Parsed Franchise, warning=FALSE}
#function returns id, first seasonid, and last seasonid and name of every team in the history of the NHL
getFranchiseInfo<- function(aName = "", aTeamId= "", aFranchiseId = ""){

#Process our inputs.  If any is non-empty, we need to add a query modifier.
#Choosing to query for FranchiseID, but could easily pull on mostRecentTeamID
fCayenneExp = ""
if(aName!="" | aTeamId != "" | aFranchiseId !="") fCayenneExp <- pullIDDecoder(aName, aTeamId, aFranchiseId)$FranchiseID
#Append the appropriate prefix for this base & endpoint
if(fCayenneExp != "") fCayenneExp <-paste0("?cayenneExp=id=",fCayenneExp)

#Define API url and pull results
fBase<- "https://records.nhl.com/site/api/"
fEndpoint<- "franchise"

#Pull API Data
fCallURL<- paste0(fBase,fEndpoint,fCayenneExp)

#Process results into a dataframe and return
fRawJSON<- GET(fCallURL)
fJSON_text<- content(fRawJSON, "text")
fParsedText <- fromJSON(fJSON_text, flatten = TRUE)
fDF <- as.data.frame(fParsedText)

return(fDF)
}
```  
### Franchise Totals  
  This endpoint tracks the accumulated stats over the entirety of a franchise's existence.  
```{r Parsed team totals}
#function Returns total stats for every franchise (ex roadTies, roadWins, etc)
getFranchiseTotals<- function(aName = "", aTeamId= "", aFranchiseId = ""){


#Process our inputs.  If any is non-empty, we need to add a query modifier.
#Need to pull for FranchiseID
fCayenneExp = ""
if(aName!="" | aTeamId != "" | aFranchiseId !="") fCayenneExp <- pullIDDecoder(aName, aTeamId, aFranchiseId)$FranchiseID
#Append the appropriate prefix for this base & endpoint
if(fCayenneExp != "") fCayenneExp <-paste0("?cayenneExp=franchiseId=",fCayenneExp)

#Define API url and pull results
fBase<- "https://records.nhl.com/site/api/"
fEndpoint<- "franchise-team-totals"

fCallURL<- paste0(fBase,fEndpoint,fCayenneExp)

#Process results into a dataframe and return
fRawJSON<- GET(fCallURL)
fJSON_text<- content(fRawJSON, "text")
fParsedText <- fromJSON(fJSON_text, flatten = TRUE)
fDF <- as.data.frame(fParsedText)

return(fDF)
}
```
### Franchise Season Records  
  This endpoint tracks the best season records for a franchise.  
```{r Parsed Franchise Season Records}
getFranchiseSeasonRecords<- function(aName = "", aTeamId= "", aFranchiseId = ""){
#Define API url and pull results
fBase<- "https://records.nhl.com/site/api/"
fEndpoint<- "franchise-season-records"

#Process our inputs.  If any is non-empty, we need to add a query modifier.
#Need to pull for FranchiseID
fCayenneExp = ""
if(aName!="" | aTeamId != "" | aFranchiseId !="") fCayenneExp <- pullIDDecoder(aName, aTeamId, aFranchiseId)$FranchiseID
#Append the appropriate prefix for this base & endpoint
if(fCayenneExp != "") fCayenneExp <-paste0("?cayenneExp=franchiseId=",fCayenneExp)

fCallURL<- paste0(fBase,fEndpoint,fCayenneExp)

#Process results into a dataframe and return
fRawJSON<- GET(fCallURL)
fJSON_text<- content(fRawJSON, "text")
fParsedText <- fromJSON(fJSON_text, flatten = TRUE)
fDF <- as.data.frame(fParsedText)

return(fDF)
}
```
### Franchise Goalie Records  
  This endpoint tracks goalie statistics during their tenure with a given francies.  Goalies will have multiple records in this endpoint across any different franchises they played with.  
```{r Parsed Goalie Records}
#Goalie records for the specified franchise 
getFranchiseGoalieRecords<- function(aName = "", aTeamId= "", aFranchiseId = ""){


#Process our inputs.  If any is non-empty, we need to add a query modifier.
#Need to pull for FranchiseID
fCayenneExp = ""
if(aName!="" | aTeamId != "" | aFranchiseId !="") fCayenneExp <- pullIDDecoder(aName, aTeamId, aFranchiseId)$FranchiseID
#Append the appropriate prefix for this base & endpoint
if(fCayenneExp != "") fCayenneExp <-paste0("?cayenneExp=franchiseId=",fCayenneExp)

#Define API url and pull results
fBase<- "https://records.nhl.com/site/api/"
fEndpoint<- "franchise-goalie-records"

fCallURL<- paste0(fBase,fEndpoint,fCayenneExp)

#Process results into a dataframe and return
fRawJSON<- GET(fCallURL)
fJSON_text<- content(fRawJSON, "text")
fParsedText <- fromJSON(fJSON_text, flatten = TRUE)
fDF <- as.data.frame(fParsedText)

return(fDF)
}
```
### Franchise Skater Records  
  This endpoint tracks single game, season, and overall statistics for offensive and defensive players during their tenures with a franchise.  Players will have multiple entries if they played for multiple franchises  
```{r Parsed Skater Records}
getFranchiseSkaterRecords<- function(aName = "", aTeamId= "", aFranchiseId = ""){
#Process our inputs.  If any is non-empty, we need to add a query modifier.
#Need to pull for FranchiseID
fCayenneExp = ""
if(aName!="" | aTeamId != "" | aFranchiseId !="") fCayenneExp <- pullIDDecoder(aName, aTeamId, aFranchiseId)$FranchiseID
#Append the appropriate prefix for this base & endpoint
if(fCayenneExp != "") fCayenneExp <-paste0("?cayenneExp=franchiseId=",fCayenneExp)

#Define API url and pull results
fBase<- "https://records.nhl.com/site/api/"
fEndpoint<- "franchise-skater-records"

fCallURL<- paste0(fBase,fEndpoint,fCayenneExp)

#Process results into a dataframe and return
fRawJSON<- GET(fCallURL)
fJSON_text<- content(fRawJSON, "text")
fParsedText <- fromJSON(fJSON_text, flatten = TRUE)
fDF <- as.data.frame(fParsedText)

return(fDF)
}
```
### Sample NHL Records Function Calls
```{r TestRecordsAPI, eval = FALSE}
#Example Calls Available for validation
gdfFranchiseAll<-getFranchiseInfo()
gdfFranchiseName<-getFranchiseInfo(aName="Devils")
gdfFranchiseNumber<-getFranchiseInfo(aFranchiseId = 2)
gdfFranchiseTeam<-getFranchiseInfo(aTeamId = 2)

gdfFranTotal<-getFranchiseTotals()
gdfFranTotalName<-getFranchiseTotals(aName="Devils")
gdfFranTotalNumber<-getFranchiseTotals(aFranchiseId = 2)
gdfFranTotalTeam<-getFranchiseTotals(aTeamId = 2)

gdfFranSeas<-getFranchiseSeasonRecords()
gdfFranSeasName<-getFranchiseSeasonRecords(aName="Devils")
gdfFranSeasNumber<-getFranchiseSeasonRecords(aFranchiseId = 2)
gdfFranSeasTeam<-getFranchiseSeasonRecords(aTeamId = 2)

gdfFranGoal<-getFranchiseGoalieRecords()
gdfFranGoalName<-getFranchiseGoalieRecords(aName="Devils")
gdfFranGoalNumber<-getFranchiseGoalieRecords(aFranchiseId = 2)
gdfFranGoalTeam<-getFranchiseGoalieRecords(aTeamId = 2)

gdfFranSkat<-getFranchiseSkaterRecords()
gdfFranSkatName<-getFranchiseSkaterRecords(aName="Devils")
gdfFranSkatNumber<-getFranchiseSkaterRecords(aFranchiseId = 2)
gdfFranSkatTeam<-getFranchiseSkaterRecords(aTeamId = 2)
```
### NHL Stats API Modifier Helper  
  Modifiers on the Stats API are less consistent.  This function takes easy hints in `aExpand` and turns them into the appropriate URL suffix.  
```{r Stats API All}
ProcessExpandArgs<- function(aExpand, aTeams)
{
  fExpand<- toupper(aExpand)
  if(fExpand == "") return("")
  if(fExpand == "ROSTER") return("?expand=team.roster")
  if(fExpand == "EZROSTER") return("?expand=person.names")
  if(fExpand == "NEXTSCHED") return("?expand=team.schedule.next")
  if(fExpand == "PREVSCHED") return("?expand=team.schedule.previous")
  if(fExpand == "STATS") return("?expand=team.stats")
  if(fExpand == "TEAMLIST") return(paste0("?teamId=", aTeams))
}
```
### NHL Stats Pull
  This API pulls information for a TeamID regarding Roster, schedules, and some statistics.  Note that most of these modifiers are pulled as dataframe columns within the returned dataframe.  This would be a good opportunity for further cleanup and development.  

  This function has three arguments in addition to the common arguments of the Records API queries.  

`aExpand` can take the following values, pulling different summary expansions:  
*"Roster", "EZRoster", "NextSched","PrevSched","Stats", "TeamList",  ""*  
A value of TeamList needs valid teamIDs. The common arguments of `aName` and `aNumber` supersede *"TeamList"*  

`aSeason` is a string formatted Y111Y222 restricting the pull to the season of interest. By default, an empty string will pull the current season where applicable. Example:  "20142015" to refer to the 2014-2015 hockey season.

`aTeams` is a comma separated string of teamIDs and requires the 'TeamList' expansion instruction. Example: "4,5,29" to pull the RecordsAPI franchise pull mostRecentTeamIDs 4,5, and 29. Note that the common inputs of `aName`, `aTeamId`, and `aFranchiseId` supersede this field  .

```{r Stats API Function}
getTeamStats<- function(aExpand="", aSeason = "", aTeams = "", 
                        aName = "", aTeamId= "", aFranchiseId = "")
{
  #Process our inputs.  If any is non-empty, we need to add a query modifier.
  #Check for a common input
  fTeamStr = ""
  if(aName!="" | aTeamId != "" | aFranchiseId !="")
    {fTeamStr <- pullIDDecoder(aName, aTeamId, aFranchiseId)$TeamID}
  #Append the appropriate prefix for this base & endpoint
  if(fTeamStr != "") fTeamStr <-paste0("/",fTeamStr)
  
    #Process aExpand and aTeams where relevant
    fExpand<- ProcessExpandArgs(aExpand, aTeams)
      
    #process aSeason
    fSeason=if(aSeason != ""){
      #If we already have a modifier, we need to tack this on with an &
      if(fExpand!="") paste0("&season=", aSeason)
      #else we need to use this as a direct modifier
      else paste0("?season=", aSeason)
    }

  #Define API url and pull results
  fBase<- "https://statsapi.web.nhl.com/api/v1/"
  fEndpoint<- "teams"

  fCallURL<- paste0(fBase,fEndpoint,fTeamStr,fExpand,fSeason)

  #Process results into a dataframe and return
  fRawJSON<- GET(fCallURL)
  fJSON_text<- content(fRawJSON, "text")
  fParsedText <- fromJSON(fJSON_text, flatten = TRUE)
  fDF <- as.data.frame(fParsedText)

  return(fDF)
}
```
### Sample calls for Stats API validation  
```{r Validate stats calls, eval = FALSE}

#Available for validation
gdfTeamStatsa<- getTeamStats(aExpand = "Roster")
gdfTeamStatsb<- getTeamStats(aExpand = "EZRoster")
gdfTeamStatsc<- getTeamStats(aExpand = "NextSched")
gdfTeamStatsd<- getTeamStats(aExpand = "PrevSChed")
gdfTeamStatse<- getTeamStats(aExpand = "Stats")
gdfTeamStatsf<- getTeamStats(aExpand = "Teamlist", aTeams = "4,5,7")
gdfTeamStatsg<- getTeamStats(aSeason = "20142015")
gdfTeamStatsh<- getTeamStats(aExpand = "Stats", aSeason = "20142015")
gdfTeamStatsi<- getTeamStats(aName = "Devils")
gdfTeamStatsj<- getTeamStats(aFranchiseId = 2)
gdfTeamStatsk<- getTeamStats(aTeamId = 2)
gdfTeamStatsl<- getTeamStats(aTeamId = "2", aTeams = "4,5,7")

gdfTeamStatsm<-getTeamStats(aName="Devils")
gdfTeamStatsn<-getTeamStats(aFranchiseId = 2)
gdfTeamStatso<-getTeamStats(aTeamId = 2)
gdfTeamStatsp<-getTeamStats()
```
### Wrapper Function to Combine Previous Endpoints  
```{r One-Stop-Wrapper Function}
pullNHLAPI<- function(aEndpoint = "", ...){
  #If we don't have any inputs, print out instructions
  #Also pull the default franchise decoder
  if(aEndpoint == ""){
    print("Please rerun with a specific endpoint chosen. Options are: ")
    print("FranchiseInfo")
    print("FranchiseTotals")
    print("FranchiseSeasonRecords")
    print("FranchiseGoalieRecords")
    print("FranchiseSkaterRecords")
    print("Team")
    print("")
    print("Common arguments to the queries are:")
    print("aName - common name of the team from FranchiseInfo pull")
    print("aTeamId - MostRecentTeamID from the FranchiseInfo pull")
    print("aFranchiseId - id field from the FranchiseInfo pull.")
    print("Note 1- aFranchiseId is constant for franchises relocating or changing names")
    print("Note 2- The \"Team\" Query has additional potential modifiers, please see vignette for more details")
    print("Vignette URL")
    return(getFranchiseInfo(...))}
  
    if(aEndpoint == "FranchiseInfo"){return(getFranchiseInfo(...))}
    if(aEndpoint == "FranchiseTotals"){return(getFranchiseTotals(...))}
    if(aEndpoint == "FranchiseSeasonRecords"){return(getFranchiseSeasonRecords(...))}
    if(aEndpoint == "FranchiseGoalieRecords"){return(getFranchiseGoalieRecords(...))}
    if(aEndpoint == "FranchiseSkaterRecords"){return(getFranchiseSkaterRecords(...))}
    if(aEndpoint == "Team"){return(getTeamStats(...))}
}
```  
### Wrapper Validation Calls
```{r Wrapper Validation, eval = FALSE}
#Available for validation
gdfWrap<- pullNHLAPI()
gdfWrapa<- pullNHLAPI("FranchiseInfo")
gdfWrapb<- pullNHLAPI("FranchiseTotals")
gdfWrapc<- pullNHLAPI("FranchiseSeasonRecords")
gdfWrapd<- pullNHLAPI("FranchiseGoalieRecords")
gdfWrape<- pullNHLAPI("FranchiseSkaterRecords")
gdfWrapf<- pullNHLAPI("Team",aName = "Devils")
gdfWrapg<- pullNHLAPI("Team", aTeamId = 2)
gdfWraph<- pullNHLAPI("Team",aFranchiseId = "2")
gdfWrapi<- pullNHLAPI("Team")
```

# Analysis - Wayne Gretzky Performance  
  I don't usually follow hockey, so this is the most that I have ever looked at hockey statistics.  From what I understand, it's mostly about scoring goals and checking people just hard enough that they don't put you in the penalty box.  Wayne Gretzky was a household name growing up.  Let's do some exploration for context about how good of a player he was.  

## Initial Pull
  Data is available in the FranchiseSkaterRecords endpoint:  

```{r Analysis_1, message=FALSE}
#Pull Data from API
gTibGretz<- as_tibble(pullNHLAPI("FranchiseSkaterRecords"))

#Flag the records that are associated with Wayne Gretzky
gTibGretz <- gTibGretz  %>% mutate(Gretzky = ifelse(data.lastName=="Gretzky" & data.firstName == "Wayne",
         "Wayne Gretzky", "Rest of League"))
```
## Filter For Players with Several Games  
  First things first, there are probably a lot of alternates, rookies, and other folks that didn't get a lot of time on the ice in this pull. Let's take a look at the distribution of games played per season and filter them out.

```{r Low Playtime}
#Create a games per season column and plot the distribution
gTibGretz<- gTibGretz %>% mutate (GamesPerSeason = data.gamesPlayed / data.seasons)
g <- ggplot(data = gTibGretz, mapping = aes(x = GamesPerSeason))
g+ geom_histogram(binwidth = 1)+ggtitle("Games Per Season for Player Franchise Records")
```

  It's a fairly uniform density, but it looks like a second mode starts around 30 games.  Let's filter out entries with <30 games per season
```{r}
gTibGretz <- gTibGretz %>% filter(GamesPerSeason >= 30)
```  
## Penalty Time vs Scoring 
Ok, now let's figure out how scoring goals correlates to penalty time.  
```{r Penalty vs Scoring, warning = FALSE}
#Scatterplot to evaluate bivariate relationship
g<- ggplot(data = gTibGretz, mapping = aes (x= data.mostPenaltyMinutesOneSeason, y = data.mostGoalsOneSeason))
g+geom_point(mapping = (aes(colour = data.positionCode, shape = Gretzky, size = Gretzky))) + 
  ggtitle("Personal Bests at a Franchise, Goals vs Penalty Time by Player, All Time")
```    
  
  We see that Wayne had a clearly phenomenal tenure at one of his franchises, apparently still being the all time scoring leader for goals in a regular season by a significant margin across all franchises.  He was also apparently very good at not getting caught checking people, as his maximum penalty time at that franchise was less than any other center who scored more than 63 goals in one season.  

  It also looks like there are four different clusters of exceptional players.  We have the Gretzky Group, who are  covert and high-scoring. These players score over 63 times in a season and have stayed under 100 minutes of penalties in a season. We also have the stadium fillers, this group is aggressive but score goals in the process.  They hang out in the penalty box 200-300 minutes in a season while scoring more than 38 goals in their best seasons.  Franchise owners probably love them, coaches probably hate them.  Second to last we have the defense and left wingers.  These guys just like hitting people and presumably remember to clear the puck from time to time.  Finally, we have some guy who managed to rack up 6 hours of penalty time in a single season -- one whole hour more than any other player has ever been tolerated by their coach.  Dave Schultz, from -- you guessed it -- Philadelphia.  

Here's the top 6 players for penalty times in a season:

```{r Max Penalty}
kable(head(gTibGretz%>% select(data.firstName, data.lastName, data.franchiseName, data.mostPenaltyMinutesOneSeason,            data.mostPenaltyMinutesSeasonIds)%>% arrange(desc((data.mostPenaltyMinutesOneSeason)))),
      format = "html",caption = "Top 6 Players - Penalty Minutes in 1 Season")
```
## Performance vs Position Played

  Alright, back to Wayne Gretzky.  We just saw that he was a center. How many skaters from different positions are we comparing against? We wouldn't want to compare that position against a defenseman for scoring. Let's generate average penalty time per game and and average goals per game to see how the different positions compare.

```{r Numerical Summaries}
#Mutate in Avg Penalty Time and Avg Goals per Game at a franchise
gTibGretz <-gTibGretz %>% mutate( penaltyMinPerGame = data.penaltyMinutes / data.gamesPlayed,
                                   goalsPerGame = data.goals/data.gamesPlayed)

gTibPositionSummary<- gTibGretz %>% group_by(data.positionCode, Gretzky) %>% 
  summarise(nPlayerFranchiseObs = n(), avgGoalsPerGame=mean(goalsPerGame),
            stdDevGoals = sd(goalsPerGame), avgPenaltyBoxPerGame = mean(penaltyMinPerGame),
            stdDevPenaltyBoxPerGame = sd(penaltyMinPerGame))

#Barchart vs Position
g<- ggplot(data = gTibPositionSummary, mapping= aes(x = data.positionCode,
                                        y = nPlayerFranchiseObs, fill = data.positionCode))
g + geom_bar( stat = 'identity' ) + ggtitle('Count of players vs position') +
  ylab('Number of Players This Position') + xlab('Position')

kable(gTibPositionSummary, digits = 3,format = "html", caption = 'Performance Summary for Each Position')
```  
  From that quick summary, we see that Centers, Left Wingers, and Right Wingers are all roughly consistent for number of points scored.  Defensemen understandably score far less.  Just from the numerical summary, we do see that Gretzky averages 3 standard deviations over the league average for a center, quite impressive.  The distribution of penaltybox times is far noisier with a coefficient of variance close to one. Gretzky is ~36% below average compared to the other Centers.  

## Offensive Player Statistics  
  Let's continue to look at where Gretzky falls relative to other offensive players.  Note that in the box plots below, we are adding some jitter to the points.  Goals, assists, and points in a single game are all whole number values, we're just adding some noise along the y-axis to help visualize point density.

```{r boxplots}
#Trim the defensive players from the set
gTibGretz <- gTibGretz %>% filter(data.positionCode%in% c('C', 'R', 'L'))

#Setup common variables for plotting
g<- ggplot(data = gTibGretz, mapping = aes(x = Gretzky, color = Gretzky))

#Individual Box Plots for several metrics
g + geom_boxplot(mapping = aes(y = goalsPerGame)) + ggtitle('Goals per Game') +
  geom_jitter(mapping = aes(y = goalsPerGame) )

g + geom_boxplot(mapping = aes(y = data.mostGoalsOneGame)) + ggtitle('Most Goals One Game') + 
  ylab('Goals in a Single Game') + geom_jitter(mapping = aes(y = data.mostGoalsOneGame))

g + geom_boxplot(mapping = aes(y = data.mostAssistsOneGame)) + ggtitle('Most Assists One Game') + 
  ylab('Assists in a Single Game') + geom_jitter(mapping = aes(y =data.mostAssistsOneGame))

g + geom_boxplot(mapping = aes(y = data.mostPointsOneGame)) + 
  ggtitle('Most Points One Game (Goals + Assists)') + ylab('Points in a Single Game') +
  geom_jitter(mapping = aes(y = data.mostPointsOneGame))

g + geom_boxplot(mapping = aes(y = penaltyMinPerGame)) + ggtitle('Average Penalty Time per Game (minutes)') + 
  ylab('Penalty Time per Game') + geom_jitter(mapping = aes(y = penaltyMinPerGame))

```  

  Clearly an exemplary player with numbers that are matched by few across his tenures at several franchises.  Let's see how his franchises performed  

```{r Analysis_2}
#Figure out which teams Gretzky Played on, and filter data table down to those franchises
gTibGretzFranchList<- gTibGretz %>% group_by(Gretzky, data.franchiseId, data.franchiseName) %>%
  summarise(offensiveSkaterCount = n(), player.gamesPlayed = max(data.gamesPlayed))

#Print the teams
kable(gTibGretzFranchList%>%select(-offensiveSkaterCount)%>%
        filter(Gretzky =="Wayne Gretzky"), format = "html", caption = "Teams Wayne Gretzky has Played For")

#Join our Gretzky decoder to the franchise records
gTibGretzkyFranch<-gTibGretzFranchList%>%
  inner_join(pullNHLAPI("FranchiseSeasonRecords"), by = "data.franchiseId")

gTibFranchSumm <- gTibGretzkyFranch %>% group_by(Gretzky) %>%
  summarise(franchiseCount = n(), averageMostGoals = mean(data.mostGoals), 
            stdDevMostGoals = sd(data.mostGoals), averageMostWins = mean(data.mostWins),
            stdDevMostWins = sd(data.mostWins), averagePenaltyTime = mean(data.mostPenaltyMinutes),
            stdDevPenaltyTime = sd(data.mostPenaltyMinutes))

kable(gTibFranchSumm, digits = 1,format = "html", caption = "Average Franchise Records for Teams Gretzky Has Not (Rest of League) and Has (Wayne Gretzky) Played for")

g<- ggplot(data = gTibGretzkyFranch, mapping = aes(x=Gretzky))

g+geom_boxplot(mapping = aes(y = data.mostGoals)) + ggtitle("Most Franchise Goals in a Season -- All Time") + 
  geom_jitter(mapping =aes(y=data.mostGoals)) 

g+geom_boxplot(mapping = aes(y = data.mostWins)) + ggtitle("Most Franchise Wins in a Season -- All Time") + 
  geom_jitter(mapping =aes(y=data.mostWins)) + ylab('Most Wins')


```
  Implied in these plots is the idea that Wayne Gretzky was playing in his franchises during all of their best years, which may be a stretch.  We've not actually limited to the seasons where Gretzky was playing for these franchises -- we're looking at all time records.  Still, I'd bet an all-time leading scorer was on the roster for at least of those franchise goal records.  For wins in a season, it looks like Gretzky's best team is in the top 7 while the others are more typical.  

## Hockey Players Named Wayne
For one last look at his influence, let's see how many skaters were named Wayne in the 2000s, ~20 years after he debuted in the NHL.

```{r Named Wayne}
#Pull a fresh, untrimmed set of skater data.  
gTibWayne<- as_tibble(pullNHLAPI("FranchiseSkaterRecords"))
#Add two factor columns for name and rough date ~20 years after Gretzky joined the Oilers
gTibWayne<- gTibWayne %>%  mutate(NamedWayne = ifelse(data.firstName == 'Wayne',"Wayne", "Not Wayne"), 
         After2000 = ifelse(as.numeric(substr(data.mostPointsSeasonIds,1,4)) > 2000, 
                            "Later than 2000", "Before 2000"))

kable(table(gTibWayne$NamedWayne, gTibWayne$After2000), format = "html",
      caption = "Players Named Wayne vs Year")
```
Allowing some buffer for kids to grow up to be NHL age, the name Wayne has not shot up in popularity in the years since Gretzky became famous.  Gretzky will have to settle for being that much more unique.  


# Recap
This vignette defines several functions for the NHL API.  More are available based on the community documentation for the [Records](https://gitlab.com/dword4/nhlapi/-/blob/master/records-api.md) and [Stats](https://gitlab.com/dword4/nhlapi/-/blob/master/stats-api.md) APIs.  There is plenty of insight available from this simple if you have a passing curiosity.  There are also far more detailed endpoints to track such things as player location throughout a game if you really want to dive deeply into it.  